---
title: "y-Randomness"
author: "Sung Inkyung"
date: '2021 1 25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Coding Credit [genuary2021: Day 19 prompt: Increase the randomness along the Y-axis by Jake Lawlor ] (https://twitter.com/Jake_Lawlor1/status/1351658324731817985)
```{r}
library(tidyverse)
library(ggforce)
library(ragg)
```


```{r practice by imitating}
n <-  20 # set number of circles
cols <-  14 # set number of columns

df1 <- 
  # make base grid
  data.frame(group = 1:(n*cols), #280
             basex = rep(c(1:cols), each = n)*4, #56
             basey = (1:n)) %>%  
  # generate randomness
  mutate(
    x = lapply(basey/2, function(x)
      {y = rnorm(4, basey, basey)
      x*c(-1, 1, 1, -1) + y}),
    y = lapply(basey/2, function(x)
    {y = rnorm(4, basey, basey)
    x*c(1, 1, -1, -1) + y})
  ) %>% 
  unnest(cols = c(x, y)) %>% 
  # add randonmnessto base grid and expand
  mutate(newy = y + basey*10.5,
         newx = x + basex*3.8)


  # plot
  plot1 <- df1 %>% 
    ggplot(aes(x = newx, y = newy,
               color = (newy),
               group = group,
               fill = (newy))) +
    geom_bspline_closed(show.legend = F,
                        alpha = .7,
                        size = .8, 
                        fill = NA) +
    coord_equal(expand = T) +
    theme_void() +
    # flip plot
    scale_y_reverse() +
    scale_color_gradient(high = "#40556b",
                         low = "#67b5af") +
    theme(panel.background = element_rect(color = "gray20",
                                          fill = "snow",
                                          size = 5),
         plot.background = element_rect(color = "black",
                                        size = .3),
         plot.margin = margin(.55, .55, .55, .55, "cm"))

```
Mark Roland
@rolandojones
·
Jan 24
Replying to 
@Jake_Lawlor1
Is there an equation for these shapes? Would you be willing to share?

Jake Lawlor
@Jake_Lawlor1
·

Sure! It's not online yet, but here's a screenshot of messy R code. Basically it's anchor points on a grid expanded into 4 corners with generated randomness incorporated, then closed B-splines around each 4-point group. 2nd pic shows a subset with anchor points.
```{r}
n <-  20 # set number of circles
cols <-  14 # set number of columns


df2 <- 
  # make base grid
  data.frame(group = 1:(n*cols), #280
             basex = rep(c(1:cols), each = n)*4, #56
             basey = (1:n)) %>% 
  # generate randomness
  mutate(
    x = lapply(basey/2, function(x)
      {y = rnorm(4, basey, basey)
      x*c(-1, 1, 1, -1) + y}),
    y = lapply(basey/2, function(x)
    {y = rnorm(4, basey, basey)
    x*c(1, 1, -1, -1) + y})
  ) %>% 
  unnest(cols = c(x, y)) %>% 
  # add randonmnessto base grid and expand
  mutate(newy = y + basey*7.5,
         newx = x + basex*2.8)

View(df2)
  # plot
 plot2 <- df2 %>% 
   ggplot(aes(x = newx, y = newy,
              color = (newy),
              group = group,
              fill = (newy))) +
   geom_bspline_closed(show.legend = F,
                       alpha = .7,
                       size = .8, 
                       fill = NA) +
   coord_equal(expand = T) +
   theme_void() +
   # flip plot
   scale_y_reverse() +
   scale_color_gradient(high = "#40556b",
                        low = "#67b5af") +
   theme(panel.background = element_rect(color = "gray20",
                                         fill = "snow",
                                         size = 5),
         plot.background = element_rect(color = "black",
                                        size = .3),
         plot.margin = margin(.55, .55, .55, .55, "cm"))
```

